
\documentclass[11pt,a4paper,sans]{moderncv}

\usepackage{verbatim}

% moderncv themes
\moderncvstyle{classic}
\moderncvcolor{green}

% character encoding
\usepackage[utf8]{inputenc}                   % replace by the encoding you are using

\usepackage[margin=.5in]{geometry}
\renewcommand*{\namefont}{\fontsize{42}{50}\mdseries\upshape}

\name{Tevin}{Jeffrey}
\address{Omitted for web}{}
\phone[fixed]{Omitted for web}
\email{tev.jeffrey@gmail.com} 
\social[linkedin]{tevinjeffrey}
\social[github]{tevjef}
\homepage{tevinjeffrey.me}

\begin{document}
\maketitle
\vspace*{-1cm}
\section{Skills}
\cvline{languages \& technologies}{Java, Go, SQL, Swift, Gradle, Kotlin, Shell, Git, Android, Espresso, RxJava, Dagger, iOS, Kubernetes, Containers, Docker, Prometheus, Grafana, PosgresSQL, Redis, Firebase, Google Cloud Platform}
\subsection{Have Experience With}
\cvline{}{C, C++, JavaScript, Python, Node.js, Amazon Web Services, gRPC, InfluxDB}

\section{Experience}
\cventry{January 2017 -- present}{Android Engineer}{Prolific Interactive}{Brooklyn, NY}{}{
\begin{itemize} \itemsep3pt \parskip0pt \parsep0pt
  \item  Collaborated with Product and UX designers on design execution feasibility and translated their \\requirements into stories/tickets for front and backend teams.
  \item Developed a MVP which saw 100K daily active users in the first week. Lead Android development \\on the product post v1.
  \item Aided in the development of our automated testing, code analysis and auditing infrastructure. 
  \item Created internal tools to automate our development workflows on Pivotal Tracker and BitBucket.
\end{itemize}}
\cventry{June -- August 2016}{Android Developer Intern}{Viacom}{New York, NY}{}{
\begin{itemize} \itemsep3pt \parskip0pt \parsep0pt
  \item Assisted in the development of Viacom's Android and Android TV applications including \\Spike, MTV, Logo TV, VH1, BET and Comedy Central
\end{itemize}}
\cventry{2009 -- 2013}{Freelance Web Designer}{99designs.com}{}{}{
\begin{itemize} \itemsep3pt \parskip0pt \parsep0pt
  \item Worked closely with dozens of clients to finalize a conceptual design for a new or revamped website.
  \item Achieved Platinum Designer rank for demonstrating the highest caliber of conceptual \\thought and technical execution in designs. 
\end{itemize}
}

\section{Projects}
\cventry{July 2016 -- present}{Rutgers Course Tracker - iOS \newline  \href{http://goo.gl/wpBtto}{Github: goo.gl/wpBtto}}{iOS SDK, Swift 3, Go, Postgres, Firebase, APNS, Protobuf}{}{}
{\begin{itemize} \itemsep3pt \parskip0pt \parsep0pt
  \item An iOS application to view Rutgers courses and subscribe to their openings.
 \item Created a Go backend consisting for several microservices running on Google Kubernetes Engine. \\Instrumented and monitored with Prometheus and Grafana.
  \item Published on the App Store: \url{http://goo.gl/4wzyS7}
\end{itemize}}

\cventry{February 2015 -- present}{Rutgers Course Tracker - Android \newline  \href{http://goo.gl/LVGis4}{Github: goo.gl/LVGis4}}{Android SDK, Dagger 2, Espresso, RxJava 2, JUnit, Mockito}{}{}
{\begin{itemize} \itemsep3pt \parskip0pt \parsep0pt
  \item An Android application to view Rutgers courses and subscribe to their openings.
  \item Built on a MVP architectural pattern and makes thoughtful use of \textbf{RxJava}, \textbf{Dagger}, \textbf{Retrofit} \\and \textbf{Android Architecture Components}.
  \item Published on Google Play: \url{http://goo.gl/7WgkV5}
\end{itemize}}

\cventry{2014 -- 2016}{Vapor for CloudApp - Android \newline \href{http://goo.gl/K9vR7K}{Github: goo.gl/K9vR7K}}{Android , Retrofit 2, Kotlin, Dagger 2, RxJava}{}{}{
\begin{itemize}
  \item An Android application to view and upload files to CloudApp's Amazon S3 buckets with an \\emphasis on making files easier to share.
  \item Rewritten to implement the lessons learned from developing Rutgers Course Tracker.
\end{itemize}}

\section{Education}
\cventry{2012-2016}{BA, Computer Science}{Rutgers, The State University of New Jersey}{Newark, NJ}{\mbox{Minor: Mathematics. GPA: 3.4 Gates Millennium Scholar}}{}

\end{document}
